Accelerating adaptive ultrasound algorithms using graphics processing units \vspace{0.5cm}

### 2014-04-05 ThesisJP/Thesis.tex
Writing background...
Changed symbol for resolution.
Writing background.
Added Paper 4.
Added paper 5.
Small cosmetic changes.
Added Paper2 and Paper3.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TITLE PAGE
\author{Jon Petter \AA{}sen}
\title{%Integrated Ultrasound Visualization and Formation
%Real-Time Adaptive Beamforming, Visualization, and Simulation 
%Real-Time Adaptive Ultrasound Algorithms
%Accelerating adaptive ultrasound algorithms using graphics processing units 
%Accelerating adaptive ultrasound algorithms with graphics processing units 
Accelerating adaptive ultrasound algorithms by means of general-purpose programming on graphics processing units 
%Accelerating adaptive ultrasound algorithms by general purpose programming on graphics processing units 
%Accelerating ultrasound algorithms with graphics processing units 
%Accelerating ultrasound algorithms using graphics processing units 
\vspace{0.5cm}}
\department{Department of Circulation and Medical Imaging}

@@

% symbol list
\usepackage{nomencl}
\makenomenclature
\renewcommand{\nomname}{Symbols and Abbreviations}
\newcommand*{\nom}[2]{#1\nomenclature{#1}{#2}}

@@

\vspace{0.3cm}
\noindent Jon Petter \AA{}sen\\
Institutt for sirkulasjon og bildediagnostikk, NTNU\\
Hovedveileder: Sverre Holm\\ 
Biveiledere: Stein-Inge Rabben, Erik Steen and Hans Torp\\
Finansieringskilde: MI-Lab

@@

\subsubsection{Acknowledgments}
\todo{Write acknowledgments ...}

@@

	\item \textbf{J.\:P.\:\AA{}sen}, J.\:I.\:Buskenes, C.-I.\:C.\:Nilsen, A.\:Austeng and S.\:Holm, "Implementing Capon Beamforming on the GPU for Real-Time Cardiac Ultrasound Imaging", {\it Proc. IEEE Ultrasonics Symposium 2012}, pp. 2133-2136.

	\item J.\:I.\:Buskenes, \textbf{J.\:P.\:\AA{}sen}, C.-I.\:C.\:Nilsen and A.\:Austeng, "Adapting the Minimum variance beamformer to a graphics processing unit for active sonar imaging systems", {\it Proc. Meetings on Acoustics 2013} vol. 13.

	\item G.\:Kiss, E.\:Steen, \textbf{J.\:P.\:\AA{}sen} and H.\:Torp, "GPU volume rendering in 3D echocardiography: real-time pre-processing and ray-casting", {\it Proc. IEEE Ultrasonics Symposium 2010}, pp. 193-196.

@@

	\item E.\:S.\:Br\o{}nstad, \textbf{J.\:P.\:\AA{}sen}, H.\:Torp and G.\:Kiss, "Visibility driven visualization of 3D cardiac ultrasound data on the GPU", {\it Proc. IEEE Ultrasonics Symposium 2012}, pp. 2651-2654.
\end{enumerate}

@@

%%%% CHAPTER 2 %%%%
\begin{bibunit}[ieeetr]
\CustChapter{Background}
\runningtitle{Background}
\input{./Background/background}
\newpage\addcontentsline{toc}{section}{References}
\putbib[./Background/background]
\end{bibunit}

@@

%%%% Paper 1 %%%%
\begin{bibunit}[ieeetr]
\CustChapterPaper{An Optimised GPU Implementation of the MVDR Beamformer for Active Sonar Imaging}
\runningtitle{GPU MVDR Beamformer for Active Sonar Imaging}
\authors{
	Jo Inge Buskenes$^{1}$, 
    	\textbf{Jon Petter \AA{}sen}$^{2}$, 
    	Carl-Inge C. Nilsen$^{1}$ and
    	Andreas Austeng$^{1}$
} 
{
	$^{1}$Department of Informatics, University of Oslo, Oslo, Norway\\
    	$^{2}$Medical Imaging Lab (MI-Lab), Norwegian University of Science and Technology, Trondheim, Norway
}
\noindent \textit{IEEE Transactions on Oceanic Engineering, accepted for publication}.
%\newpage\input{./CaponSonarGPU/CaponSonarGPU}
%\newpage\addcontentsline{toc}{section}{References}
%\putbib[./CaponSonarGPU/bibCaponSonarGPU]
\end{bibunit}

%%%% Paper 2 %%%%
\begin{bibunit}[ieeetr]
\CustChapterPaper{Implementing Capon Beamforming on a GPU for Real-Time Cardiac Ultrasound Imaging}
\runningtitle{GPU Capon Beamformer for Cardiac Ultrasound Imaging}
\authors{
	\textbf{Jon Petter \AA{}sen}$^{1}$,
    	Jo Inge Buskenes$^{2}$,  
    	Carl-Inge C. Nilsen$^{2}$,
    	Andreas Austeng$^{2}$ and
    	Sverre Holm$^{1,2}$
} 
{
	$^{1}$Medical Imaging Lab (MI-Lab), Norwegian University of Science and Technology, Trondheim, Norway\\
    	$^{2}$Department of Informatics, University of Oslo, Oslo, Norway
}
\noindent \textit{IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, vol. 61, pp. 76-85, Jan 2014}.
%\input{./CaponCardiacGPU/CaponCardiacGPU}
%\newpage\addcontentsline{toc}{section}{References}
%\putbib[./CaponCardiacGPU/bibCaponCardiacGPU]
\end{bibunit}

%%%% Paper 3 %%%%
\begin{bibunit}[ieeetr]
\CustChapterPaper{Capon Beamforming and Moving Objects - An Analysis of Lateral Shift-Invariance}
\runningtitle{Capon Beamforming and Moving Objects}
\authors{
	\textbf{Jon Petter \AA{}sen}$^{1}$, 
    	Andreas Austeng$^{2}$ and
    	Sverre Holm$^{1,2}$
} 
{
	$^{1}$Medical Imaging Lab (MI-Lab), Norwegian University of Science and Technology, Trondheim, Norway\\
    	$^{2}$Department of Informatics, University of Oslo, Oslo, Norway
}
\noindent \textit{IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, accepted for publication}.
%\input{./CaponMovingObjects/CaponMovingObjects}
%\newpage\addcontentsline{toc}{section}{References}
%\putbib[./CaponMovingObjects/bibCaponMovingObjects]
\end{bibunit}

%%%% Paper 4 %%%%
\begin{bibunit}[ieeetr]
\CustChapterPaper{Adaptive Volume Rendering of Cardiac 3D Ultrasound Images - Utilizing Blood Pool Statistics}
\runningtitle{Adaptive Volume Rendering of Cardiac Ultrasound}
\authors{
	\textbf{Jon Petter \AA{}sen}$^{1}$,
	Erik Steen$^2$,
	Gabriel Kiss$^{3,4}$,
	Anders Thorstensen$^{1,5}$,
	Stein Inge Rabben$^2$
}
{
$^{1}$Medical Imaging Lab (MI-Lab), Norwegian University of Science and Technology, Trondheim, Norway\\
$^{2}$ GE Vingmed Ultrasound, Horten, Norway\\
$^{3}$ Norwegian University of Science and Technology, ISB - Department of Circulation and Medical Imaging, Trondheim, Norway\\
$^{4}$ St. Olavs Hospital, Trondheim, Norway\\
$^{5}$ Department of Cardiology, St. Olavs Hospital, Trondheim, Norway
}
\noindent \textit{Proc. SPIE Medical Imaging 2012, vol. 8320, pp. 832008.}
%\input{./AdaptiveVolumeRendering/AdaptiveVolumeRendering}
%\newpage\addcontentsline{toc}{section}{References}
%\putbib[./AdaptiveVolumeRendering/bibAdaptiveVolumeRendering]
\end{bibunit}

%%%% Paper 5 %%%%
\begin{bibunit}[ieeetr]
\CustChapterPaper{Huygens on Speed: Interactive Simulation of Ultrasound Pressure Fields}
\runningtitle{Huygens on speed}
\authors{\textbf{Jon Petter \AA{}sen}$^1$ and Sverre Holm$^{1,2}$}
{
	$^{1}$Medical Imaging Lab (MI-Lab), Norwegian University of Science and Technology, Trondheim, Norway\\
    	$^{2}$Department of Informatics, University of Oslo, Oslo, Norway
}
\noindent \textit{Proc. IEEE Ultrasonics Symposium 2012, pp. 1643-1646}.
%\input{./Hos/Hos}
%\newpage\addcontentsline{toc}{section}{References}
%\putbib[./Hos/bibHos]
\end{bibunit}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TITLE PAGE
\author{Jon Petter Helgesen \AA{}sen}
\title{%Integrated Ultrasound Visualization and Formation
%Real-Time Adaptive Beamforming, Visualization, and Simulation 
%Real-Time Adaptive Ultrasound Algorithms
%Accelerating adaptive ultrasound algorithms using graphics processing units 
%Accelerating adaptive ultrasound algorithms with graphics processing units 
Accelerating adaptive ultrasound imaging algorithms by means of general-purpose computing on graphics processing units 
%Accelerating adaptive ultrasound algorithms by general purpose programming on graphics processing units 
%Accelerating ultrasound algorithms with graphics processing units 
%Accelerating ultrasound algorithms using graphics processing units 
\vspace{0.5cm}}
\department{Department of Circulation and Medical Imaging}

@@

% from Paper 3
\usepackage{epstopdf}

% from spie.tex (Paper 4)
\usepackage{array}

% from hos (Paper 5)
\usepackage{url}
%\usepackage{epsfig}

% symbol list
\usepackage{nomencl}
\makenomenclature
\renewcommand{\nomname}{Symbols and Abbreviations}
\newcommand*{\nom}[2]{#1\nomenclature{#1}{#2}}
\newcommand*{\nomi}[2]{\nomenclature{#1}{#2}}

@@

\vspace{0.3cm}
\noindent Jon Petter Helgesen \AA{}sen\\
Institutt for sirkulasjon og bildediagnostikk, NTNU\\
Hovedveileder: Sverre Holm\\ 
Biveiledere: Stein-Inge Rabben, Erik Steen and Hans Torp\\
Finansieringskilde: MI-Lab

@@

\subsubsection{Acknowledgments}
\todo{Write acknowledgments ...}
Takkeliste: Beate. Farmor. Familien. Andreas Austeng. Jo Inge Buskenes. Carl-Inge Colombo Nilsen. Ines Hafizovic for feedback on the introduction and background. Sverre Holm. Miljøet i Trondheim. PhD studentene i Trondheim spesielt. Miljøet i Oslo. Miljøet hos Vingmed. SquareHead.

@@

	\item \textbf{J.\:P.\:\AA{}sen}, J.\:I.\:Buskenes, C.-I.\:C.\:Nilsen, A.\:Austeng and S.\:Holm, "Implementing Capon Beamforming on the GPU for Real-Time Cardiac Ultrasound Imaging", {\it Proc. IEEE Ultrasonics Symposium 2012, pp. 2133-2136}.

	\item J.\:I.\:Buskenes, \textbf{J.\:P.\:\AA{}sen}, C.-I.\:C.\:Nilsen and A.\:Austeng, "Adapting the Minimum variance beamformer to a graphics processing unit for active sonar imaging systems", {\it Proc. Meetings on Acoustics 2013, vol. 13}. \textit{Invited talk}.

	\item G.\:Kiss, E.\:Steen, \textbf{J.\:P.\:\AA{}sen} and H.\:Torp, "GPU volume rendering in 3D echocardiography: real-time pre-processing and ray-casting", {\it Proc. IEEE Ultrasonics Symposium 2010, pp. 193-196}.

@@

	\item E.\:S.\:Br\o{}nstad, \textbf{J.\:P.\:\AA{}sen}, H.\:Torp and G.\:Kiss, "Visibility driven visualization of 3D cardiac ultrasound data on the GPU", {\it Proc. IEEE Ultrasonics Symposium 2012, pp. 2651-2654}.
\end{enumerate}

@@

%%%% CHAPTER 2 %%%%
\begin{bibunit}[IEEEtran]
\CustChapter{Background}
\runningtitle{Background}
\input{./Background/background}
\newpage\addcontentsline{toc}{section}{References}
\putbib[./Background/background]
\end{bibunit}

@@

%%%% Paper 1 %%%%
\begin{bibunit}[IEEEtran]
\CustChapterPaper{An Optimised GPU Implementation of the MVDR Beamformer for Active Sonar Imaging}
\runningtitle{GPU MVDR Beamformer for Active Sonar Imaging}
\authors{
	Jo Inge Buskenes$^{1}$, 
    	\textbf{Jon Petter \AA{}sen}$^{2}$, 
    	Carl-Inge C. Nilsen$^{1}$ and
    	Andreas Austeng$^{1}$
} 
{
	$^{1}$Department of Informatics, University of Oslo, Oslo, Norway\\
    	$^{2}$Medical Imaging Lab (MI-Lab), Norwegian University of Science and Technology, Trondheim, Norway
}
\noindent \textit{IEEE Transactions on Oceanic Engineering, accepted for publication}.
%\newpage\input{./CaponSonarGPU/CaponSonarGPU}
%\newpage\addcontentsline{toc}{section}{References}
%\putbib[./CaponSonarGPU/bibCaponSonarGPU]
\end{bibunit}

%%%% Paper 2 %%%%
\begin{bibunit}[IEEEtran]
\CustChapterPaper{Implementing Capon Beamforming on a GPU for Real-Time Cardiac Ultrasound Imaging}
\runningtitle{GPU Capon Beamformer for Cardiac Ultrasound Imaging}
\authors{
	\textbf{Jon Petter \AA{}sen}$^{1}$,
    	Jo Inge Buskenes$^{2}$,  
    	Carl-Inge C. Nilsen$^{2}$,
    	Andreas Austeng$^{2}$ and
    	Sverre Holm$^{1,2}$
} 
{
	$^{1}$Medical Imaging Lab (MI-Lab), Norwegian University of Science and Technology, Trondheim, Norway\\
    	$^{2}$Department of Informatics, University of Oslo, Oslo, Norway
}
\noindent \textit{IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, vol. 61, pp. 76-85, Jan 2014}.
\newpage
{\input{./Paper2/cos}}
\newpage
\addcontentsline{toc}{section}{References}
\putbib[./Paper2/cosbib]
\end{bibunit}

%%%% Paper 3 %%%%
\begin{bibunit}[IEEEtran]
\CustChapterPaper{Capon Beamforming and Moving Objects - An Analysis of Lateral Shift-Invariance}
\runningtitle{Capon Beamforming and Moving Objects}
\authors{
	\textbf{Jon Petter \AA{}sen}$^{1}$, 
    	Andreas Austeng$^{2}$ and
    	Sverre Holm$^{1,2}$
} 
{
	$^{1}$Medical Imaging Lab (MI-Lab), Norwegian University of Science and Technology, Trondheim, Norway\\
    	$^{2}$Department of Informatics, University of Oslo, Oslo, Norway
}
\noindent \textit{IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, accepted for publication}.
\newpage\input{./Paper3/moving_obj}
\newpage\addcontentsline{toc}{section}{References}
\putbib[./Paper3/moving_objbib]
\end{bibunit}

%%%% Paper 4 %%%%
\begin{bibunit}[IEEEtran]
\CustChapterPaper{Adaptive Volume Rendering of Cardiac 3D Ultrasound Images - Utilizing Blood Pool Statistics}
\runningtitle{Adaptive Volume Rendering of Cardiac Ultrasound}
\authors{
	\textbf{Jon Petter \AA{}sen}$^{1}$,
	Erik Steen$^2$,
	Gabriel Kiss$^{3,4}$,
	Anders Thorstensen$^{1,5}$,
	Stein Inge Rabben$^2$
}
{
$^{1}$Medical Imaging Lab (MI-Lab), Norwegian University of Science and Technology, Trondheim, Norway\\
$^{2}$ GE Vingmed Ultrasound, Horten, Norway\\
$^{3}$ Norwegian University of Science and Technology, ISB - Department of Circulation and Medical Imaging, Trondheim, Norway\\
$^{4}$ St. Olavs Hospital, Trondheim, Norway\\
$^{5}$ Department of Cardiology, St. Olavs Hospital, Trondheim, Norway
}
\noindent \textit{Proc. SPIE Medical Imaging 2012, vol. 8320, pp. 832008.}
\newpage\input{./Paper4/spie}
\newpage\addcontentsline{toc}{section}{References}
\putbib[./Paper4/spiebib]
\end{bibunit}

%%%% Paper 5 %%%%
\begin{bibunit}[IEEEtran]
\CustChapterPaper{Huygens on Speed: Interactive Simulation of Ultrasound Pressure Fields}
\runningtitle{Huygens on speed}
\authors{\textbf{Jon Petter \AA{}sen}$^1$ and Sverre Holm$^{1,2}$}
{
	$^{1}$Medical Imaging Lab (MI-Lab), Norwegian University of Science and Technology, Trondheim, Norway\\
    	$^{2}$Department of Informatics, University of Oslo, Oslo, Norway
}
\noindent \textit{Proc. IEEE Ultrasonics Symposium 2012, pp. 1643-1646}.
\newpage\input{./Paper5/hos}
\newpage\addcontentsline{toc}{section}{References}
\putbib[./Paper5/hosbib]
\end{bibunit}
